WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-04-10 article/Article.tex
add bugtracker url and reference
darcs-hash:20060405145241-2fc9d-b2a2fc6c9c6e35f9d422e1abfb5b61027fbbbd05.gz
article continued
darcs-hash:20060410155846-2fc9d-29b6f0fc7eca3e02d23dceb170673d564602a13e.gz

Currently, WrapITK have been tested on Mandriva Linux \cite{MandrivaWebSite}, and MacOS X, and only
supports Python properly; Java and Tcl libraries build
correctly but the Java and Tcl support classes for loading these libraries is
entirely out of date and is not working.

@@

@@

    \subsubsection{Get the software}

@@

To get the last version from the darcs repository can be obtained
with the command 
\verb$darcs get http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/$.

For the user who don't want to use darcs \cite{DarcsWebSite} but want the last development version,
a nightly updated archive is available at
\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/WrapITK.tar.gz}.

WrapITK requires ITK and CableSwig to have been previously downloaded and built.
To get CableSwig, simply run:
\verb$cvs -d:pserver:anonymous@public.kitware.com:/cvsroot/CableSwig co CableSwig$
(Note that no cvs login is needed here.)

    \subsubsection{Required and optional patches}

@@

@@

@@

Here is the list of itk classes which can currently be substituted by python sequences:
\begin{itemize}
  \item \verb$CovariantVector$
  \item \verb$FixedArray$
  \item \verb$Index$
  \item \verb$Offset$
  \item \verb$Size$
  \item \verb$Vector$
  \item \verb$ContinuousIndex$
\end{itemize}

@@

External projects let the developer access some custom class with the target languages
and is a powerful way to extend WrapITK, test new wrapper, wrap more types, etc.
A nice side effect of wrappers, for contributions\footnote{A nice template for
contributions to the Insight Journal \cite{InsightJournalWebSite} which include the 
template code to build wrappers is available at
\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/template/}. Just use the command
{\em darcs get http://voxel.jouy.inra.fr/darcs/contrib-itk/template/ contribName}
and edit the project name in the {\em CMakeLists.txt} file to
begin your new contribution.} for example, is to build {\em all}
the methods of the wrapped classes, and so to be sure everything builds as it should
\footnote{We have found and fixed numbers of bug in ITK while adding
more classes to WrapITK}.

@@

More examples can be found in the contributions to the Insight Journal
\cite{InsightJournalWebSite}, or directly at \url{http://voxel.jouy.inra.fr/darcsweb/}.

@@

WrapITK is an opensource project, and so all contributions are welcome. Here are
some points which requires special attention:
\begin{itemize}
  \item Test it and report problem. That's the more important thing to do:
we need feedbacks to enhance WrapITK quality !
  \item Work on tcl, java, and others. We are not tcl or java developers, and so
are not able to complete the work for those languages. Any help from tcl and
java expert would be highly appreciated. Also, there is no reason to be limited
to python, tcl and java, and WrapITK can be extended to other languages supported
by swig like perl \cite{PerlWebSite}, ruby \cite{RubyWebSite}, ocaml \cite{OcamlWebSite} and others.
  \item Add more classes. WrapITK add lots of new classes compared to the current
wrapping system, but there is still lots of work to do, especially to support more
filter dedicated to \verb$Vector$ pixels.
\end{itemize}

\verb$darcs$ \cite{DarcsWebSite} allow to easily contribute to WrapITK, by sending patch by email with
the command \verb$darcs send$, while keeping credits for the work done.
Feel free to send patches; they will be tested and integrated in the project.

@@

>>>>

@@

\section{Supported languages and plateforms}

Java, Tcl and Python builds properly and are fully usable. However, Java and
Tcl don't yet have the extended features added to Python\footnote{Any help
to extend Java and Tcl support would be higly appreciated.}.

WrapITK is mainly developed on Mandriva Linux \cite{MandrivaWebSite} and 
MacOS X \cite{MacOsXWebSite} and so is well tested on this palteforms.
It also builds on windows \cite{WindowsWebSite}, but require more testing
to be sure everything work as it should. See below for details about how
to report bugs are contribute patches.

Several tests are available\footnote{There is currently 49 tests with the default
configuration.} for Python, Tcl and Java. They can be run with the \verb$ctest$
command.

\section{Performance}

@@

    \subsubsection{Get the software sources}

@@

The last version can be obtained from the development repository with darcs \cite{DarcsWebSite}.
The command is
\verb$darcs get --partial http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/$\footnote{Note
that the {\em --partial} option is required on systems with case insensitive filesystem like
windows or Mac Os X.}.

For the user who don't want to use darcs \cite{DarcsWebSite} but still want the last development version,
a nightly updated archive is available at
\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/WrapITK.tar.gz}.

    \subsubsection{ITK}

@@

WrapITK requires ITK and CableSwig \cite{ITKWebSite} to have been previously downloaded and built.
To get a development version of CableSwig, simply run:
\verb$cvs -d:pserver:anonymous@public.kitware.com:/cvsroot/CableSwig co CableSwig$
(Note that no cvs login is needed here.)

    \subsubsection{Python}

Python \cite{PythonWebSite} is required only to build python support.
WrapITK is reported to work with python 2.3 and python 2.4. However, the test framework
requires the \verb$subprocess$ module available in standard only in python 2.4 and above.
To run the python test with python 2.3, you have to install \verb$subprocess$.

    \subsubsection{Tcl}

Tcl \cite{TclWebSite} is required only to build tcl support.
WrapITK have been tested with Tcl 8.4.11.

    \subsubsection{Java}

Java \cite{JavaWebSite} is required only to build java support.
WrapITK have been tested with java \verb$1.5.0_06-b05$.

@@

    \subsubsection{Binary packages}

@@

Here is the list of itk classes which can currently be substituted by python sequences:
\begin{itemize}
  \item \verb$Array$
  \item \verb$ContinuousIndex$
  \item \verb$CovariantVector$
  \item \verb$FixedArray$
  \item \verb$Index$
  \item \verb$Offset$
  \item \verb$Size$
  \item \verb$Vector$
\end{itemize}

@@

External projects let the developer access some custom class with the target languages
and is a powerful way to extend WrapITK, test new wrapper, wrap more types, etc.
A nice side effect of wrappers, for contributions\footnote{A nice template for
contributions to the Insight Journal \cite{InsightJournalWebSite} which include the 
template code to build wrappers is available at
\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/template/}. Just use the command
{\em darcs get http://voxel.jouy.inra.fr/darcs/contrib-itk/template/ contribName}
and edit the project name in the {\em CMakeLists.txt} file to
begin your new contribution.} for example, is to build {\em all}
the methods of the wrapped classes, and so to be sure everything builds as it should
\footnote{We have found and fixed numbers of bug in ITK while adding
more classes to WrapITK}.
In WrapITK, we used them to avoid managing switches if some dependencies or not
found: the project must found this dependencies or fail.

@@

More examples can be found in the contributions to the Insight Journal
\cite{InsightJournalWebSite}, or directly at \url{http://voxel.jouy.inra.fr/darcs/contrib-itk/}.

@@

WrapITK is an opensource project, and so all contributions are welcome. Here are
some points which requires special attention:
\begin{itemize}
  \item Test it and report problem. That's the more important thing to do:
we need feedbacks to enhance WrapITK quality ! Report all bugs you may found
to \url{http://voxel.jouy.inra.fr/roundup/wrapitk/} \cite{RoundupWebSite}.
  \item Work on tcl, java, and others. We are not tcl or java developers, and so
are not able to complete the work for those languages. Any help from tcl and
java expert would be highly appreciated. Also, there is no reason to be limited
to python, tcl and java, and WrapITK can be extended to other languages supported
by swig like perl \cite{PerlWebSite}, ruby \cite{RubyWebSite}, ocaml \cite{OcamlWebSite} and others.
  \item Add more classes. WrapITK add lots of new classes compared to the current
wrapping system, but there is still lots of work to do, especially to support more
filter dedicated to \verb$Vector$ pixels.
\end{itemize}

\verb$darcs$ \cite{DarcsWebSite} allow to easily contribute to WrapITK, by sending
patch by email, while keeping credits for the work done.
Feel free to send patches; they will be tested and integrated in the project.

The basic commands to know are:
\begin{itemize}

  \item \verb$darcs get --partial http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/$
to get a copy of WrapITK repository.

  \item \verb$darcs whatsnew$ to display the changes you have done in
your copy of the repository.

  \item \verb$darcs record$ to record the changes you have made in your
copy of the repository. darcs will propose you to select some changes
to record. It is better to create one patch for each feature or bug
fix, rather than one big patch for all your current changes.

  \item \verb$darcs send$ to send by email the patches you have recorded with
\verb$darcs record$.
% TODO: which email adress ??

Read the {\em Getting started} section of the darcs manual \cite{DarcsWebSite}
for more information.

@@

We thank Andr\'e Bongers.
